Automated Topic Naming

### 2012-01-19 ese/ese.tex
abram hates commas

% NEIL --> Explain the reason why this sentence is included: 
%It should be noted that much of PostgreSQL development originates from
%the project mailing list, and the developers are often pushing integrations. 
If we compare the global NFR distribution (that is, the relative global frequency of each NFR label)
to each author we find that 25\%
 of the authors have a similarity (Pearson correlation) of $0.47$ or less. In other words, for these authors (gathered to the lower left of Figure  \ref{fig:authorsim}),
 their NFR distribution does not match well with the global
 distribution.
Authors \texttt{momjian} and \texttt{tgl} are in the top right of
Figure \ref{fig:authorsim}
    top right, dominate in topic count and commit count, thus they are
    very similar to the global distribution of NFR topics.
Figure \ref{fig:authorsim} demonstrates that although a  few authors dominate in
the number of commits many authors exhibit different behaviour in
terms of the NFR-relevant topics of their commits. Furthermore there
are no authors in the top left corner, indicating that the authors who
commit less, do not contribute with a similar NFR-topic distribution
as \texttt{momjian} or \texttt{tgl}.
We found that number of commits correlated with an author's similarity to the
global NFR distribution ($0.59$ Pearson), i.e., the variables ``number of topics associated with a developer'' and ``number of commits'' are not discriminative.

>>>>

% NEIL --> Explain the reason why this sentence is included: 
%It should be noted that much of PostgreSQL development originates from
%the project mailing list, and the developers are often pushing integrations. 
If we compare the global NFR distribution (that is, the relative global frequency of each NFR label)
to each author we find that 25\%
 of the authors have a similarity (Pearson correlation) of $0.47$ or less. In other words, for these authors (gathered to the lower left of Figure  \ref{fig:authorsim}),
 their NFR distribution does not match well with the global
 distribution.
Authors \texttt{momjian} and \texttt{tgl} are in the top right of
Figure \ref{fig:authorsim}, dominate in topic count and commit count, and so are
    very similar to the global distribution of NFR topics.
Figure \ref{fig:authorsim} demonstrates that although a  few authors dominate in
the number of commits, many authors exhibit different behaviour in
terms of the NFR-relevant topics of their commits. Furthermore, there
are no authors in the top left corner, indicating that the authors who
commit less, do not contribute with a similar NFR-topic distribution
as \texttt{momjian} or \texttt{tgl}.
We found that number of commits correlated with an author's similarity to the
global NFR distribution ($0.59$ Pearson), i.e., the variables ``number of topics associated with a developer'' and ``number of commits'' are not discriminative.
